### 2019-03-18 papers/journal/encoding.tex
sd

In this section we will present the $\fsmt$, $\fbmc$ and $\fqbf$ search encodings with the encoding for synthesis problem. We will start with the $\fsmt$ search encoding and later present the contrast with the $\fbmc$ encoding.

\subsection{$\fsmt$ search encoding}
\label{enc:smt}

@@

\subsection{$\fbmc$ search encoding}

Our first attempt was to encode the existential condition check as a $\fbmc$ search problem.
%
%In this section we will present the $\fbmc$ encoding of the same.
%
Although the techniques used for $\fbmc$ and $\fsmt$ is very different because we are not unrolling the complete program in the case of $\fbmc$, the encoding is not considerably different.
% 
The $\fbmc$ search encoding differs with the presented $\fsmt$ encoding in the way variables are represented and how we encode reachability (both for the stability and connectivity).  
%
Here, we will only present the stability encoding.
%the rest of the encodings are similar to the one presented in the previous section, Section~\ref{enc:smt}.

@@

\subsection{Universal condition}
\label{enc:univ-cond}
%
Recall that the specification for universal condition~\ref{sec:property} requires quantifier alternation. 
%
Most SAT solvers can not efficiently handle the quantifier in the formulas. 
% 
Although, it is possible to encode the universal condition as a SAT or SMT problem.
%
There is always a danger of a blow-up in the formula size, making it harder for the SAT solver to handle. 
%Which may blow up the formula size for the solver to solve.
% 
As an experiment, we have implemented a direct SMT version of the universal problem extending the current $\fsmt$ search encodings.
%
The basic idea is to conjunct the formula for each combination value of the quantified variable. 
%
%
\input{satqbf-table}
%
The table~\ref{tab:satqbf-graph}, shows the search results of this encoding for the universal condition with 5 nodes and 3-connected graphs. 
%
The SMT extended version was not able to scale it to the desired results and either timed-out (T/O) or ran out of memory (M/O).
%
This can be due to the fact that directly translating a quantified formula into a quantifier-free  by introducing a vector of variables for each boolean possibility will blow up the size of the formula and may not be solvable by a solver.
%

@@

\subsection{Synthesis of VTS}
In this section, we will present our synthesis method for
the synthesis problems.
%
%We assume that certain properties of the partial input VTS always hold, for example, the activity of the molecules and well-fused constraints. 
%
%Whereas properties like stability and connectivity discussed in the previous sections may not.
%
Here, we use these two properties stability and connectivity against which we perform our synthesis. 
%
The encoding can be easily extended to accommodate other interesting properties.

>>>>

In the previous section, we have discussed four problems.
%
In this section we will present encodings fof the
$\fsmt$ search, $\fbmc$ search, $\fqbf$ search and synthesis problems.
%
We will start with the $\fsmt$ search encoding and later present the
contrast with the $\fbmc$ encoding.

\subsection{Encoding for $\fsmt$ search problem}
\label{enc:smt}

@@

\subsection{Encoding for $\fbmc$ search problem}

Our first attempt was to encode the existential condition check as a $\fbmc$ search problem~\cite{plospaper}.
%
%In this section we will present the $\fbmc$ encoding of the same.
%
Although the techniques used for $\fbmc$ and $\fsmt$ is very different because we are not unrolling the complete program in the case of $\fbmc$, the encoding is not considerably different.
% 
The $\fbmc$ search encoding differs with the presented $\fsmt$ encoding in the way variables are represented and how we encode reachability (both for the stability and connectivity).  
%
Here, we will only present the stability encoding.
%the rest of the encodings are similar to the one presented in the previous section, Section~\ref{enc:smt}.

@@

\subsection{Encoding for $\fqbf$ search problem}
\label{enc:univ-cond}
%
Recall that the specification for universal condition~\ref{sec:property} requires quantifier alternation. 
%
Most SAT solvers can not efficiently handle the quantifier in the formulas. 
% 
Although, it is possible to encode the universal condition as a SAT or SMT problem.
%
There is always a danger of a blow-up in the formula size, making it harder for the SAT solver to handle. 
%Which may blow up the formula size for the solver to solve.
% 
As an experiment, we have implemented a direct SMT version of the universal problem extending the current $\fsmt$ search encodings.
%
The basic idea is to conjunct the formula for each combination value of the quantified variable. 
%
%
\input{satqbf-table}
%
The table~\ref{tab:satqbf-graph}, shows the search results of this encoding for the universal condition with 5 nodes and 3-connected graphs. 
%
The SMT extended version was not able to scale it to the desired results and either timed-out (T/O) or ran out of memory (M/O).
%
This can be due to the fact that directly translating a quantified formula into a quantifier-free  by introducing a vector of variables for each boolean possibility will blow up the size of the formula and may not be solvable by a solver.
%

@@

\subsection{Encoding for the synthesis problem}
In this section, we will present our synthesis method for
the synthesis problems.
%
%We assume that certain properties of the partial input VTS always hold, for example, the activity of the molecules and well-fused constraints. 
%
%Whereas properties like stability and connectivity discussed in the previous sections may not.
%
Here, we use these two properties stability and connectivity against which we perform our synthesis. 
%
The encoding can be easily extended to accommodate other interesting properties.

### 2019-03-18 papers/journal/problem.tex
sd

This section will present the different search problems of VTS.
%
We categorize the search problems into three different categories, search problem for existential condition, search problem for universal condition and performing synthesis on the incomplete VTS.

@@

%\subsection{Problem Statements}
\subsection{Synthesis of VTS}
We will assume that we are given a VTS, whose all components
are not specified.
%
Our objective is to find the missing parts.
%
The missing parts can be in any of the components of VTS. 
%
For example, some undiscovered edges or nodes, or insufficient
knowledge about the presence of molecules in some part of the VTS.
%
To cover most of the likely variations of this missing information,
we have encoded the following variants of VTS synthesis problem.

@@

\subsubsection{Encoding synthesis property}

We will do synthesis against the property that the VTS
is stable and 3-connected.
%
% The property is designed to balance the search space such that the synthesis procedure does not
% succeed with simply adding too many edges. 
%
%\begin{align*}
%\texttt{Property} =  \texttt{Stability} \land \texttt{Connected}(3) 
%%\land \texttt{DisConnected}(4)
%\end{align*}
This property was proposed in~\cite{shukla2017discovering}.
%
However, the biological relevance of the property is debatable and open for change.
%
Our tool is easily modifiable to support any other property that may be deemed 
interesting by the biologists.

>>>>

This section will present the different search problems of VTS.
%
We categorize the search problems into three different categories, search problem for existential condition, search problem for universal condition,
and performing synthesis on the incomplete VTS.

@@

%\subsection{Problem Statements}
\subsection{Synthesis of VTS}
%
We also consider another variant of analysis of VTSs.
%
We will assume that we are given a VTS, whose all components
are not specified.
%
Our objective is to find the missing parts.
%
The missing parts can be in any of the components of VTS. 
%
For example, some undiscovered edges or nodes, or insufficient
knowledge about the presence of molecules in some part of the VTS.
%
To cover most of the likely variations of this missing information,
we have encoded the following variants of VTS synthesis problem.

@@

\subsubsection{Synthesis problem}

We will do synthesis against the property that the VTS
is stable and 3-connected.
%
% The property is designed to balance the search space such that the synthesis procedure does not
% succeed with simply adding too many edges. 
%
%\begin{align*}
%\texttt{Property} =  \texttt{Stability} \land \texttt{Connected}(3) 
%%\land \texttt{DisConnected}(4)
%\end{align*}
This property was proposed in~\cite{shukla2017discovering}.
%
However, the biological relevance of the property is debatable and open for change.
%
% Our tool is easily modifiable to support any other property that may be deemed 
% interesting by the biologists.

### 2019-03-18 papers/journal/property.tex
Minor updates on synthesis code
Vts dia update
sd

\ankit{This section requires a revision}
We analyze the model against our desired properties.
%
Since in biology there are are no declared specifications or properties,
we conjecture some properties that appear to be true in all known
biological systems.
%
In this paper, we choose graph connectedness to be a key property.
%
We will also seek two kinds of questions give the property.

@@

The goal is to find the minimum graph connectivity properties that for each of the condition.

>>>>

%\ankit{This section needs a revision}
We analyze the model against our desired properties.
%
Since in biology there are no declared specifications or properties,
we conjecture some properties that appear to be true in all the known
biological systems.
%
In this paper, we choose graph connectedness to be a key property.
%
We will also seek two kinds of questions give the property.

@@

The goal is to find the minimum graph connectivity properties for each of the condition.
